SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Add future development section on pydata/sparse

\textbf{Future development}.
\textit{This section should include key issues: sparse arrays, ndimage pixel vs point, splines, fftpack vs. np.fft and linalg vs. np.linalg, under-maintained submodules.}

>>>>

\textbf{Future development}.
Future development plans include a major rewrite of the \texttt{scipy.sparse} module, which is already underway\cite{abbasi2018sparse}. This is due to the current interface only supporting two dimensional objects. Even sub-arrays are two dimensional, and dimensions greater than two aren't supported. The new package lacks performance, but it does support dimensions greater than two and a number of other useful features.

\textit{This section should include key issues: sparse arrays, ndimage pixel vs point, splines, fftpack vs. np.fft and linalg vs. np.linalg, under-maintained submodules.}
